Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method

### 2020-11-06 odrr5d/paper.tex
2020年11月 6日 星期五 01时36分29秒 CST

%\inputdir{./}
%\plot{field_d0_0}{width=0.8\textwidth}{Real data example \new{with a lot of missing traces}. \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here. The two transparent colored windows denote two zooming areas for an amplified comparison.}}
%
%\plot{field_dn_N12_0}{width=0.8\textwidth}{Real data example. (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=20$. \new{It is obvious that all three methods obtain dramatic improvement from the raw data. The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
%\plot{field_dn_N12_z1}{width=0.8\textwidth}{Zoomed comparison for the field data example (the blue frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method.}
%\plot{field_dn_N12_z2}{width=0.8\textwidth}{Zoomed comparison for the field data example (the red frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method.}
%\plot{field_dn_N12_t80}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.32$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method.}
%\plot{field_dn_N12_t160}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.64$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
}

>>>>

\inputdir{./}
\plot{field_d0_0}{width=0.8\textwidth}{Real data example \new{with a lot of missing traces}. \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here. The two transparent colored windows denote two zooming areas for an amplified comparison.}}

\plot{field_dn_N12_0}{width=0.8\textwidth}{Real data example. (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=20$. \new{It is obvious that all three methods obtain dramatic improvement from the raw data. The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
\plot{field_dn_N12_z1}{width=0.8\textwidth}{Zoomed comparison for the field data example (the blue frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method.}
\plot{field_dn_N12_z2}{width=0.8\textwidth}{Zoomed comparison for the field data example (the red frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method.}
\plot{field_dn_N12_t80}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.32$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method.}
\plot{field_dn_N12_t160}{width=0.8\textwidth}{Comparison for constant time slice for the field data example ($t=0.64$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
}
